---
title: "Documentation"
output: html_document
---

In this part, I will implement linear regression with one variable to predict profits for a food truck.Suppose you are the CEO of a restaurant franchise and are considering different cities for opening a new outlet. The chain already has trucks in various cities and you have data for profits and populations from the cities.


You would like to use this data to help you select which city to expand to next.

The file data1.txt contains the dataset for our linear regression. The first column is the population of a city and the second column is the profit of a food truck in that city. A negative value for profit indicates a loss.


Library Packages:
```{r library packages,results=FALSE}
library(ggplot2)
```

Let's see the original data first,there are two columns representing Population of City in 10,000s and Profit in $10,000s.

```{r readdata}
data<-read.table("data1.txt",sep=",",header = F)
names(data)<-c("population","profit")
head(data)
summary(data)
```

Plotting: 

It is often useful to understand the data by visualizing it. For this dataset, we can use a scatter plot to visualize the data.
```{r, plotting}
ggplot(data,aes(x=population,y=profit))+geom_point(colour="red",size=3)+geom_smooth(type="lm")
```

Linear Regression,get the intercept and slope of the "best" straight line.

```{r linearreg}
fit<-lm(profit~population,data=data)
summary(fit)
intercept<-fit$coefficients[1]
slope<-fit$coefficients[2]
```

Prediction

```{r prediction}
predict_population=11.03
predict_profit=slope*predict_population+intercept
predict_profit
```

Conclusion

In this project, I implement linear regression and get to see it work on data about the profit changed by the population of the city.
